---
title: "Video Game Analysis"
author: "Kuldeep Parashar"
date: "02/01/2019"

output: 
  html_document:
  
    toc: true # table of content true
    toc_depth: 3  # upto three depths of headings (specified by #, ## and ###)
    number_sections: true  ## if you want number sections at each table header
    theme: united  # many options for theme, this one is my favorite.
    highlight: tango  # specifies the syntax highlighting style
    #css: my.css   # you can add your custom css, should be in same folder

---

```{r, echo=FALSE}
htmltools::img(src = knitr::image_uri(file.path("/Users/kuldeep/Documents/GitHub/render_medium/docs/Blue3.jpg")), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px;')
```

---


## Whats its all About?

This is an exhaustive analytic report for getting a clear insight on the video game industry, from its very primitive stage to the peak of the video game industry.The data set is from `Kaggle`

This report answers Questions on Video Game industries. Some of them are Stated below:

* >which platform has the most game available? 

* >which company has the most profitable Video game?

* >What share of market is held by companies in different regions?


### Introducing Our Source `The Data`

```{r results='hide',message=FALSE,echo=FALSE,warning=FALSE}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(plotly)

setwd("/Users/kuldeep/Desktop/Deploy")
main_df<-read_csv("/Users/kuldeep/Downloads/vgsales.csv",na=c("Na","N/A","NA","na","  "))
df<-main_df
summary(df)
dim(df)
library(rlang)
```
The data is in Csv(Comma Separated) format,the dimensions are `r< dim(df) >`.
The names of all the columns and their meanings are stated below:-
```{r echo=FALSE,results='asis'}
library(knitr)
library(kableExtra)
name<-names(df)
name<-as.data.frame(name)
colnames(name)<-"Atrributes"
name["meanings"]<-c("Rank of video game","Name of video game","Platform for which it is developed","Year of release","type of game","Publisher/Developing Company","North Amrica total Sales","Europe total Sales","Japan Sales","Sales in all other Countries","Global total Sales")
kable(name)%>%
  kable_styling(bootstrap_options = c("striped", "hover","bordered", "condensed"),full_width = F)%>%column_spec(2,background ="#BSB8B6")
```
There are missing data in the csv so we have to clean the data and also tidy it. 

### Data Wrangling

Data Wrangling is the term collectively given to Data Cleaning And Data Tidying
In this process we do the following things :-

* Check data Consistency,duplicates
* Check for Missing Data
* Check For Outlines 
* Find a strong reason before removing Outliers
* Fill the Missing Values
* Fill the the corrupted Data with proper data
* Feature Engineering-process of making new Features 

Lets get hands on  to this:-

First converting all the character into factor so that we can easily implement Statistics modelling function and also it would be handy to use them in plotting libraries like ggplot2   

```{r echo=FALSE,results='hide',message=FALSE,echo=FALSE,warning=FALSE}
df<-as.data.frame(df)
for(i in 3:6)
{
  df[,i]<-as.factor(df[,i])
}
```
nNw we can see that categorical data are interpreted by R,
when we look at the data  we see that 'N/A' is used for representing NA, if we did not change it, R will not recognize it as a Missing value and we get error prone results.

```{r message=FALSE,echo=FALSE,warning=FALSE}
summary(df)
```
Now we will check the consistency of the data, whether tha data inside a column is homogeneous or not, or the data inside column is feasible or not.

taking the mean of the differences between the actualSale calculated by summing up Sales from all countries to the Global_Sale Attributes we get
```{r message=FALSE,echo=FALSE,warning=FALSE}

mean(df[,length(names(df))]-(df[,length(names(df))-1]+df[,length(names(df))-2]+df[,length(names(df))-3]+df[,length(names(df))-4]))

```


So from here we can see that the Global_sale atrribute is not correct and has some errors in it. Since the value in revenue is in million dollars, so there is significant amount of data which is entered false. Lets change the value of the Global_sale with the sum of Japan sale,North America Sale,Europe Sale and others sale. 

```{r message=FALSE,echo=FALSE,warning=FALSE}
tot_val<-as.data.frame(df[,length(names(df))-1]+df[,length(names(df))-2]+df[,length(names(df))-3]+df[,length(names(df))-4])
colnames(tot_val)<-"total_Sale"
tot_val<-cbind(tot_val,df[,length(names(df))])
ggplot(data = tot_val)+geom_freqpoly(mapping=aes(x=tot_val$total_Sale),color="red",alpha=0.8,stat_bin=10)+geom_freqpoly(mapping = aes(x=df[, length(names(df))]),color="green")



```
The long tail in the graph clearly states that there are only very few games which have total revenue greater then 75.Most probably these are the most popular game, if not so it may be an outlier.Also we have to check for the duplicacy of the data.
```{r message=FALSE,echo=FALSE,warning=FALSE }
df%>%group_by(Name)%>%summarise(count=n())%>%filter(count>1)%>%arrange(desc(count))
library(tidyverse)
```
So here we can see that there are 2,775 videogames which are being published more than once, surely these game must have great revenue thats why there are multiple releases.


In the next section we will analysis the trend and try to find the correlations and give answer to various Curious Questions too.



### Univariate
So here we see that how the data is being spread, and its central tendencies to get  direct insight of the data

#### Yearly Increase in Videogame Development
```{r message=FALSE,echo=FALSE,warning=FALSE}
library(tidyverse)
library(dplyr)
df<-na.omit(df)
summary(df$Year)
  plot<-ggplot(data = df,aes(x=df$Year,position="Fill",fill=df$Genre))+geom_bar()+coord_flip()
ggplotly(plot)
```
The hisogram clearly states that there is an abrupt declination in video game manufacturing from  2012, this also act as an evidence that there are very less jobs for video game developer in 2014.
The graph fall abruptly after 2016, this indicates that there must be some kind of problem in data gathering after 2016, the data is inconsistent.We will limit our studies till 2016. 

#### Genre wise No. of Game Developed 
This graphs shows which, which genre have most no. games in it .Action Games are at the tops followed by Sports, here interesting insights is that, miscellaneous game are 3rd highest ranking. 
```{r  message=FALSE,echo=FALSE,warning=FALSE}
library(forcats)
plo2<-ggplot(data = df,aes(x=fct_infreq(Genre),fill=df$Genre))+geom_bar()+coord_flip()
ggplotly(plo2)
```
This graphs shows which, which genre have most number of games in it. Action Games are at the tops followed by Sports, here interesting insights is that, miscellenious game are 3rd highest ranking.

#### game Genre distribution on Countries
Lets see distribution of companies developing game in a Genre.   

#### Sales Country wise Analysis
```{r results='hide',message=FALSE,echo=FALSE,warning=FALSE ,collapse=TRUE}
jap_sale<-sum(df$JP_Sales)
Eu_sal<-sum(df$EU_Sales)
Na_Sale<-sum(df$NA_Sales)
other<-sum(df$Other_Sales)

plot_df<-data.frame(c("Japan","Europe","NorthAmerica","other_sale"),c(jap_sale,Eu_sal,Na_Sale,other))

colnames(plot_df)<-c("Country","Total_sales")
plot2<-ggplot(data=plot_df,aes(x=Country,y=Total_sales))+geom_count(mapping = aes(color=Country))
plot2
```

From here we can clearly say that most of the sales come from the North America but if we think from the  point of view of Marketing its not a great metric, as we know that Japan has less population so if we incorporate that factor into metric, things may be different.



## Get Some insights  {.tabset}

### Top 10 Revenue generating Games
To do the left work and mark things together:
```{r message=FALSE,echo=FALSE,warning=FALSE}

top_20_max_rev<-df%>%group_by(Name)%>%summarise(total_sale=sum(Global_Sales))%>%arrange(desc(total_sale))%>%top_n(10)
kable(top_20_max_rev)%>%
  kable_styling(bootstrap_options = c("striped", "hover","bordered", "condensed"),full_width = F)%>%column_spec(2,background ="#BSB8B6")
```
So till 2016 these games have the most global revenue, Wii sports which is a nentando game is on the top and google search link also state this (Quite interesting actually)
GrandTheft Auto is on 2 followed by Super Mario.

```{r message=FALSE,echo=FALSE,warning=FALSE}
Name_vd<-ggplot(data=top_20_max_rev,aes(x=Name,y=total_sale))+geom_point(size=2,mapping = aes(color=total_sale))+coord_flip()
ggplotly(Name_vd)
```

### Top 5 Revenue Generating Genres
For a Game developer finding the sweet spot is important to make revenue in such a competitive market. Lets first find which genre generates maximum revenue and after that we will find that which genre has least competition that is, total revenue divided by total number of video game companies making games on that genre.
```{r message=FALSE,echo=FALSE,warning=FALSE}
top_10_genre<-df%>%group_by(Genre)%>%summarise(total_revenue=sum(Global_Sales))%>%top_n(12)%>%arrange(desc(total_revenue))

kable(top_10_genre)%>%
kable_styling(bootstrap_options = c("striped", "hover","bordered", "condensed"),full_width = F)%>%column_spec(2,background ="#BSB8B6")
```
Here we can see that Misc genre is on 3 position in number of count of games but in of case revenue generation its far from genre like Action, Sports and all. 
```{r message=FALSE,echo=FALSE,warning=FALSE}

genre<-ggplot(data=top_10_genre,aes(x=Genre,y=total_revenue))+geom_point(size=2,mapping = aes(color=total_revenue))+coord_flip()

ggplotly(genre)
```

### Sweet Spot!!

Now lets find that which genre has the least number of video games developed in it.

The metric would be like, total revenue generate by a genre divided by the total number of  video game in that genre.

```{r message=FALSE,echo=FALSE,warning=FALSE}
Mtric_ease<-df%>%group_by(Genre)%>%summarise(total_revenue=sum(Global_Sales),count=n(),ease_metric=total_revenue/count)%>%arrange(desc(ease_metric))
kable(Mtric_ease)%>%
kable_styling(bootstrap_options = c("striped", "hover","bordered", "condensed"),full_width = F)%>%column_spec(2,background ="#BSB8B6")

```
Some interesting facts: as we can see that Platorm and Shotter game are generating great average revenue per game, action game clearly gets out of top 5 and it clearly shows that there are a lot of games,

```{r message=FALSE,echo=FALSE,warning=FALSE}

genre<-ggplot(data=Mtric_ease)+geom_point(mapping = aes(x=Genre,y=ease_metric,color=ease_metric))+coord_flip()

ggplotly(genre)
```

### Facts on Consoles!!

Lets find that which Console offers the most number of video games.
Ease metric gives us that an Average revenue generated by a Game launched for a console type.

```{r message=FALSE,echo=FALSE,warning=FALSE}
Mtric_ease_cons<-df%>%group_by(Platform)%>%summarise(total_revenue=sum(Global_Sales),count=n(),ease_metric=total_revenue/count)%>%arrange(desc(total_revenue,count,ease_metric))
kable(Mtric_ease_cons%>%filter(count>15))%>%
kable_styling(bootstrap_options = c("striped", "hover","bordered", "condensed"),full_width = F)%>%column_spec(2,background ="#BSB8B6")

```
The above table clearly indicates that the PS range of console by sony has generated the maximum revenue, so for increasing sales for the video game one must make the video game compatible with top revenue generating console which is large in number.

The plot gives a clear insight of the revenue generated by a specific console.
```{r message=FALSE,echo=FALSE,warning=FALSE}
Cons_plot<-ggplot(data =Mtric_ease_cons)+geom_point(mapping = aes(x=Platform,y=total_revenue,color=total_revenue))+coord_flip()
ggplotly(Cons_plot)
```
But taking Revenue as a metric for compatibility may be distorted as it might be possible that bacause of one specific kind of game revenue has increased but the number of Console is less, so comapatiblity priority must be choosen by taking both factors revenue and the count of console.